Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-26 tex/background.tex
tweak text on physics context

In recent years, polar dielectrics such as Silicon Carbide (SiC) have caught the attention of researchers as an alternative to plasmonic metals, 
due to their low optical losses in in the mid- to long-wave infrared range. 
Nanostructures made of these materials offer sensing capabilities, described by their \emph{figure of merits}, that are unattainable with plasmonic metals. 
The figure of merits of a nanoparticle is defined as the ratio between the sensitivity and the width of the resonance peak at mid-height \cite{otte-etal-2012}. 
In turn, sensitivity is the shift in the resonance position divided by the change in the refractive index: 
$S = \Delta \lambda / \Delta n$.
The dielectric of these materials has a negative real part and a very small imaginary part, in the mid/long infrared region. 
This dielectric behavior is similar to that observed in metals like silver in the blue part of the wavelength spectrum. 
In plasmonics, when illuminating a small particle made of metallic materials, we will observe that certain wavelengths excite a surface plasmon. 
The main difference with polar dielectrics like SiC is that for this material the frequency of the incoming light matches instead the resonance frequency of the Si and C sub-lattices \cite{caldwell2015,rockstuhl2005}. 
This excitation leads to a strong extinction cross-section at the resonance wavelength, and an enhanced near-field amplitude. 
These behaviors can be modeled with the same approaches used for localized surface plasmon resonance, and when the wavelength is much larger than the size
of the nanoparticle, we can again apply the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.

When studying both surface phonon polaritons and surface plasmon resonances, we can analyze the spectrums by measuring different quantities. 
We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
These different approaches are comparable since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen. 
Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.

>>>>

In recent years, polar dielectric crystals such as Silicon Carbide (SiC) became recognized as an alternative to plasmonic metals in many technologies, including biosensors. 
They manifest oscillations of lattice-bound charges, called surface phonon polaritons, in the mid- to long-wave infrared range with low optical losses.
Nanostructures made of these materials offer sensing capabilities, described by their \emph{figure of merits}, that are unattainable with plasmonic metals. 
The figure of merits of a nanoparticle is defined as the ratio between the sensitivity and the width of the resonance peak at mid-height \cite{otte-etal-2012}. 
In turn, sensitivity is the shift in the resonance position divided by the change in the refractive index: 
$S = \Delta \lambda / \Delta n$.
The dielectric function of polar dielectrics has a negative real part and a small imaginary part, in the mid to long infrared regime. 
This dielectric behavior is similar to that observed in metals like silver in the blue part of the wavelength spectrum. 
In plasmonics, when illuminating a small particle made of metallic materials, we will observe that certain wavelengths excite a surface plasmon. 
The main difference with polar dielectrics like SiC is that for this material the frequency of the incoming light matches instead the resonance frequency of the Si and C sub-lattices \cite{caldwell2015,rockstuhl2005}. 
This excitation leads to a strong extinction cross-section at the resonance wavelength, and an enhanced near-field amplitude. 
These behaviors can be modeled with the same approaches used for localized surface plasmon resonance, and when the wavelength is much larger than the size
of the nanoparticle, we can again apply the electrostatic approach implemented in \pygbe \cite{ClementiETal2017, ClementiETal2019}.

When studying both surface phonon polaritons and surface plasmon resonances, one can analyze the spectrums by measuring different quantities. 
We can measure scattering cross-section, extinction cross-section (scattering plus absorption), as well as reflection. 
These different approaches are comparable since the \textit{quantity of interest} is the wavelength (frequency) at which the resonance modes happen. 
Whether we measure reflection or extinction cross-section, the wavelength (frequency) at which the peaks happen remains the same. 
Throughout this work, we will concentrate on studying the wavelength (frequency) at which the resonance modes occur, 
and we aim to replicate results from Rockstuhl et al.\ 2005 \cite{rockstuhl2005} and from Ellis et al.\ 2016 \cite{ellis2016}, 
and to validate our software against experimental results from Ellis et al.\ 2016 \cite{ellis2016}.
